MCC Models

### 2020-08-10 papers/full_paper/manuscript.Rmd
advance revision

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Leipzig Research Center for Early Child Development, Jahnallee 59, 04109 Leipzig, Germany"
    email         : "manuel.bohn@uni-leipzig.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "3"
  - name          : "Megan Merrick"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
  - id            : "3"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"

@@

These examples, however, highlight children’s use of a single pragmatic information source or cue. Harnessing multiple – potentially competing – cues poses a separate challenge. One aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance. Much less is known about whether and how children combine these types of information. Developmental studies that look at the integration of multiple information sources more generally find that children are sensitive to multiple sources from early on [@graham2017words; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers]. For example, in a classic study, Nadig and Sedivy [-@nadig2002evidence] found that children rapidly integrate information provided in an utterance (a particular referring expression) with the speaker’s perspective (the objects the speaker can see). However, the information sources to be integrated in these studies are not all pragmatic in nature. Children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not their ability to reason about the speaker’s intention in context. As a consequence, this work does not speak to the question of how and if listeners integrate different forms of *pragmatic* information. Thus, while many theories of pragmatic reasoning presuppose that pragmatic information sources are integrated, the nature of their relationship has typically not been specified.

@@

How is information integrated in this context in this context? The *integration model* assumes that the informativeness of an utterance depends on the common ground shared between interlocutors. That is, the listener assumes that the speaker takes the common ground shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance. As a consequence, when prior interactions strongly implicate one object as the more likely referent (for example in the preference - same speaker conditions in experiment 3, 4 and 7), the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground. Taken together, this model provides an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning. Predictions generated based on this process accurately captured adults' inferences across a wide range of conditions.

>>>>

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Leipzig Research Center for Early Child Development, Jahnallee 59, 04109 Leipzig, Germany"
    email         : "manuel.bohn@uni-leipzig.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "4"
  - name          : "Megan Merrick"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
  - id            : "3"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
  - id            : "4"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"

@@

These examples, however, highlight children’s use of a single pragmatic information source or cue. Harnessing multiple – potentially competing – pragmatic cues poses a separate challenge. One aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance. Much less is known about whether and how children combine these types of information. Developmental studies that look at the integration of multiple information sources more generally find that children are sensitive to multiple sources from early on [@graham2017words; @grosse201021; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @ganea2007infants]. For example, in a classic study, Nadig and Sedivy [-@nadig2002evidence] found that children rapidly integrate information provided in an utterance (a particular referring expression) with the speaker’s perspective (the objects the speaker can see). However, the information sources to be integrated in these studies are not all pragmatic in nature. Children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not necessarily their ability to reason about the speaker’s intention in context. As a consequence, this work does not speak to the question of how and if listeners integrate different forms of *pragmatic* information. Thus, while many theories of pragmatic reasoning presuppose that pragmatic information sources are integrated, the nature of their relationship has typically not been specified.

@@

How is information integrated in this context in this context? The *integration model* assumes that the informativeness of an utterance depends on the common ground shared between interlocutors. That is, the listener assumes that the speaker takes the common ground shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance. As a consequence, when prior interactions strongly implicate one object as the more likely referent (for example in the preference - same speaker conditions in experiment 3, 4 and 7), the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground. Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@brunder1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning. Predictions generated based on this process accurately captured adults' inferences across a wide range of conditions.
